Draft TLF generator

### 2023-04-26 posts/manipulate/draft_tlf_generator.qmd
Update draft_tlf_generator.qmd

Get all the needed datasets from metadata
```{r}
domains <- purrr::map(tlfp$tlfmetadata, ~purrr::pluck(.x, "domains"))  |>
        purrr::list_simplify()  |>
        unique()
```

@@

```{r}
#| echo: true
#| eval: false
tlfp$get("demographic_example2")
```
```{r}
#| echo: false
#| eval: true
#| message: FALSE
table_to_html(tlfp$get("demographic_example2"), to_html = FALSE)
```

the size of tlfp
```{r}
print(object.size(tlfp))
```

Transform the class of `rtables`
```{r}
table_to_dataframe <- function(tbl) {

>>>>

- Get all the needed datasets from metadata
```{r}
domains <- purrr::map(tlfp$tlfmetadata, ~purrr::pluck(.x, "domains"))  |>
        purrr::list_simplify()  |>
        unique()
```

@@

```{r}
#| echo: true
#| eval: false
tlfp$get("demographic_example2")
```
```{r}
#| echo: false
#| eval: true
#| message: FALSE
table_to_html(tlfp$get("demographic_example2"), to_html = FALSE)
```
&nbsp;

- the size of tlfp
```{r}
print(object.size(tlfp))
```

- Transform the class of `rtables`
```{r}
table_to_dataframe <- function(tbl) {
